\renewcommand{\bibname}{References}

\begin{thebibliography}{90}

\addcontentsline{toc}{chapter}{References}

\bibitem[Miller 1997]{recmake}
  P. Miller,
  \emph{Recursive make considered harmful},
  1997.

\bibitem[Wikimedia e.a. 2014]{wikixslfo}
  \emph{XSL Formatting Objects},
  Wikimedia Foundation, Inc. e.a., 
  \url{http://en.wikipedia.org/wiki/XSL\_Formatting\_Objects},
  Last visited 24 september 2014.

\bibitem[Refsnes Data 2014]{w3schoolxslfo}
  \emph{XSL-FO Pages},
  Refsnes Data,
  1999 - 2014,
  \url{http://www.w3schools.com/xslfo/xslfo\_pages.asp},
  Last visited 24 september 2014.

\bibitem[Weaver \& Smith 2012]{xutools}
  Gabriel A. Weaver and Sean W. Smith,
  `XUTools: Unix Commands for Processing Next-Generation Structured Text'
  \emph{Presented as part of the 26th Large Installation System Administration Conference (LISA 12)},
  USENIX,
  p. 83-99,
  2012,
  \url{http://www.w3schools.com/xslfo/xslfo\_pages.asp},
  Last visited 24 september 2014.
  
\bibitem[European Commission 2014]{web-content-syndication}
    European Commission, 
    \emph{Web Content Syndication},
    \url{http://ec.europa.eu/ipg/standards/markup/web-content-syndication/index\_en.htm}, visited 24/09/2014.
    
\bibitem[RSS (Wikipedia]{rss-wiki}
    Wikipedia,
    \emph{RSS},
    \url{http://en.wikipedia.org/wiki/RSS}, last visited 24/09/2014.

\bibitem[Reg\(exp\)\{2\}lained]{regex-explained}
	Lea Verou,
	\emph{Reg\(exp\)\{2\}lained},
	\url{http://www.youtube.com/watch?v=EkluES9Rvak}, 08/04/2013.

\bibitem[Regexx Lookahead and Lookbehind]{regex-lookaround}
    Regexx,
    \emph{Mastering lookahead and lookbehind},
	\url{http://www.rexegg.com/regex-lookarounds.html}, last visited 24/09/2014.

\bibitem[Tech Talk: Linus Torvalds on git]{linus-git}
    Linus Torvald on Git,
    \emph{Google Tech Talk: Linus Torvalds on git},
	\url{https://www.youtube.com/watch?v=4XpnKHJAok8},14/04/2007.
	
\bibitem[Git software wikipedia]{git-wiki}
    Wikipedia,
    \emph{Git},
    \url{http://en.wikipedia.org/wiki/Git\_(software)}, last visited 24/09/2014.
    
\bibitem[SHA-1 Wikipedia]{sha-1-attacks-wiki}
    Wikipedia,
    \emph{SHA-1 attacks},
    \url{http://en.wikipedia.org/wiki/SHA-1#Attacks}, last visited 24/09/2014.

\end{thebibliography}
